Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-02 overleaf/results.tex
shrank the graphs

\begin{figure*}[htbp]
\centering
%\resizebox{7in}{!}{\input{graphs/lan/all-hist-OnlineSetupTimesec}}
\input{graphs/lan/all-hist-OnlineSetupTimesec}
\caption{Circuit Evaluation Time (Setup + Online) of Benchmarks}
\label{fig:graph_all_eval_time}
\end{figure*}

@@

\begin{figure}[htbp]
\centering
\resizebox{3.6in}{!}{\input{graphs/lan/biometric-hist-OnlineSetupTimesec}}
\caption{Biometric Matching Circuit Evaluation Time, x-axis lists database size}
\label{fig:graph_biometric_eval_time}
\end{figure}

\begin{figure}[htbp]
\centering
\resizebox{3.6in}{!}{\input{graphs/lan/biometric-hist-CommunicationMiB}}
\caption{Biometric Matching Communication Size, x-axis lists database size}
\label{fig:graph_biometic_comm_size}
\end{figure}

\begin{figure}[htbp]
\centering
\resizebox{3.6in}{!}{\input{graphs/lan/biometric-hist-CircuitGenerationTimesec}}
\caption{Biometric Matching Circuit Generation Time, x-axis lists database size}
\label{fig:graph_biometic_circ_gen_time}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\resizebox{3.6in}{!}{\input{graphs/comparison-hist-OnlineSetupTimesec}}
\caption{LAN vs. WAN: Circuit Evaluation Time Comparison}
\label{fig:graph_comparison_eval_time}
\end{figure}

@@

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-CommunicationMiB}
\caption{Communication Size of Benchmarks}
\label{fig:graph_comm_size}
\end{figure*}

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-CircuitGenerationTimesec}
\caption{Circuit Generation Time of Benchmarks}
\label{fig:graph_circ_gen_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-TotalGates}
\caption{Number of Gates of Benchmarks}
\label{fig:graph_total_gates}
\end{figure*}

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-OnlineTimesec}
\caption{Online Time of Benchmarks}
\label{fig:graph_online_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\input{graphs/lan/all-hist-SetupTimesec}
\caption{Setup Time of Benchmarks}
\label{fig:graph_setup_time}
\end{figure*}

\subsection{Comparison with MOTION-native Inner Product and Discussion}

>>>>

\begin{figure*}[htbp]
\centering
%\resizebox{7in}{!}{\input{graphs/lan/all-hist-OnlineSetupTimesec}}
\resizebox{0.7\textwidth}{!}{\input{graphs/lan/all-hist-OnlineSetupTimesec}}
\caption{Circuit Evaluation Time (Setup + Online) of Benchmarks}
\label{fig:graph_all_eval_time}
\end{figure*}

@@

\begin{figure}[htbp]
\centering
\resizebox{0.7\columnwidth}{!}{\input{graphs/lan/biometric-hist-OnlineSetupTimesec}}
\caption{Biometric Matching Circuit Evaluation Time, x-axis lists database size}
\label{fig:graph_biometric_eval_time}
\end{figure}

\begin{figure}[htbp]
\centering
\resizebox{0.7\columnwidth}{!}{\input{graphs/lan/biometric-hist-CommunicationMiB}}
\caption{Biometric Matching Communication Size, x-axis lists database size}
\label{fig:graph_biometic_comm_size}
\end{figure}

\begin{figure}[htbp]
\centering
\resizebox{0.7\columnwidth}{!}{\input{graphs/lan/biometric-hist-CircuitGenerationTimesec}}
\caption{Biometric Matching Circuit Generation Time, x-axis lists database size}
\label{fig:graph_biometic_circ_gen_time}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\resizebox{0.7\columnwidth}{!}{\input{graphs/comparison-hist-OnlineSetupTimesec}}
\caption{LAN vs. WAN: Circuit Evaluation Time Comparison}
\label{fig:graph_comparison_eval_time}
\end{figure}

@@

\begin{figure*}[htbp]
\centering
\resizebox{0.7\textwidth}{!}{\input{graphs/lan/all-hist-CommunicationMiB}}
\caption{Communication Size of Benchmarks}
\label{fig:graph_comm_size}
\end{figure*}

\begin{figure*}[htbp]
\centering
\resizebox{0.7\textwidth}{!}{\input{graphs/lan/all-hist-CircuitGenerationTimesec}}
\caption{Circuit Generation Time of Benchmarks}
\label{fig:graph_circ_gen_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\resizebox{0.7\textwidth}{!}{\input{graphs/lan/all-hist-TotalGates}}
\caption{Number of Gates of Benchmarks}
\label{fig:graph_total_gates}
\end{figure*}

\begin{figure*}[htbp]
\centering
\resizebox{0.7\textwidth}{!}{\input{graphs/lan/all-hist-OnlineTimesec}}
\caption{Online Time of Benchmarks}
\label{fig:graph_online_time}
\end{figure*}

\begin{figure*}[htbp]
\centering
\resizebox{0.7\textwidth}{!}{\input{graphs/lan/all-hist-SetupTimesec}}
\caption{Setup Time of Benchmarks}
\label{fig:graph_setup_time}
\end{figure*}

\subsection{Comparison with MOTION-native Inner Product}
